Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-10 S3_run_simulations_EE_not_last.Rmd
make model fitting optional

```{r fit models}
## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  targetFname <-  paste0(fitDir,"/fits_", scenario, "_obs.rda")
  if(!file.exists(targetFname)){
    fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
    save(fits, file =targetFname, compress = "xz")

@@

  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
```

>>>>

```{r fit models}
fit_models  <- FALSE
if(fit_models){
  ## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
  pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
    targetFname <-  paste0(fitDir,"/fits_", scenario, "_obs.rda")
    if(!file.exists(targetFname)){
      fits <- fit_life_histories(scenario = scenario,
                               birth_level_data = data_births_monthly)
      save(fits, file =targetFname, compress = "xz")

@@

    }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
}
